Test

### 2016-07-22 Berkeley_PD_Stop.Rmd

stop_df <- separate(stop_df, Dispositions, into = c("Individual_1", "Individual_2", "Individual_3", "Individual_4", "Individual_5"), extra = "merge", fill = "right")

stop_df <- melt(stop_df, id = c("Incident.Number", "Call.Date.Time", "Location", "Incident.Type", "Other")) %>%
  arrange(Incident.Number)

@@

=======

>>>>

# Creating new entries for multiple people in one disposition
stop_df <- stop_df %>%
  separate(Dispositions, into = c("1", "2", "3", "4", "5"), extra = "merge", fill = 
             "right") %>%
  gather(key = Individual, value = Dispositions, -Incident.Type, -Incident.Number, -Call.Date.Time, -Location, -Other) %>%
  na.omit() %>%
  arrange(Incident.Number)

@@
